smooth-sea

### 2018-05-22 index.rmd
removing transition for avp scatter

The goal of this research is to a.) understand the temporal dynamics of rent estimates in Seattle and b.) forecast the current quarter's rent levels based off of the prior periods. Throughout the following analyses, the training data are 2017 Q2 up to the prior quarter (i.e. `r as.yearqtr(Sys.Date())-.25`). The test period is a forecast for the current period and includes comparison to the appropriate median rent estimates for data observed so far in this period.

@@

```{r, echo=F}
avp_scatter <- ggplot(sea_df, aes(x = actualRent, y = nsar1_Med, size = n1B, frame = listingQtr)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  scale_x_continuous(labels = scales::dollar) +
  scale_y_continuous(labels = scales::dollar) +
  xlab("\nActual") +
  ylab("Predicted\n") +
  scale_size_area() +
  coord_equal() +
  theme_minimal()

ggplotly(avp_scatter) %>%
  layout(autosize = T, margin = list(b = 50, r = 50, l = 50, t = 50)) %>%
  animation_opts(1000, easing = "linear", redraw = FALSE)
```

@@

```{r, echo=F}
avp_scatter <- ggplot(sea_df, aes(x = actualRent, y = bym_Med, size = n1B, frame = listingQtr)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  scale_x_continuous(labels = scales::dollar) +
  scale_y_continuous(labels = scales::dollar) +
  xlab("\nActual") +
  ylab("Predicted\n") +
  scale_size_area() +
  coord_equal() +
  theme_minimal()

ggplotly(avp_scatter) %>%
  layout(autosize = T, margin = list(b = 50, r = 50, l = 50, t = 50)) %>%
  animation_opts(1000, easing = "linear", redraw = FALSE)
```

@@

```{r, echo=F}
avp_scatter <- ggplot(sea_df, aes(x = actualRent, y = spt_Med, size = n1B, frame = listingQtr)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  scale_x_continuous(labels = scales::dollar) +
  scale_y_continuous(labels = scales::dollar) +
  xlab("\nActual") +
  ylab("Predicted\n") +
  scale_size_area() +
  coord_equal() +
  theme_minimal()

ggplotly(avp_scatter) %>%
  layout(autosize = T, margin = list(b = 50, r = 50, l = 50, t = 50)) %>%
  animation_opts(1000, easing = "linear", redraw = FALSE)
```

>>>>

The goal of this research is to a.) understand the temporal dynamics of rent estimates in Seattle and b.) forecast the current quarter's rent levels based off of the prior periods. Throughout the following analyses, the training data are `r min(sea_df$listingQtr)` up to the prior quarter (i.e. `r as.yearqtr(Sys.Date())-.25`). The test period is a forecast for the current period and includes comparison to the appropriate median rent estimates for data observed so far in this period.

@@

```{r, echo=F}
avp_scatter <- ggplot(sea_df, aes(x = actualRent, y = nsar1_Med, size = n1B, frame = listingQtr)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  scale_x_continuous(labels = scales::dollar) +
  scale_y_continuous(labels = scales::dollar) +
  xlab("Actual\n") +
  ylab("\nPredicted") +
  scale_size_area() +
  coord_equal() +
  theme_minimal()

ggplotly(avp_scatter) %>%
  layout(autosize = T, margin = list(b = 50, r = 50, l = 50, t = 50)) %>%
  animation_opts(1000, transition = 0, redraw = T)
```

@@

```{r, echo=F}
avp_scatter <- ggplot(sea_df, aes(x = actualRent, y = bym_Med, size = n1B, frame = listingQtr)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  scale_x_continuous(labels = scales::dollar) +
  scale_y_continuous(labels = scales::dollar) +
  xlab("Actual\n") +
  ylab("\nPredicted") +
  scale_size_area() +
  coord_equal() +
  theme_minimal()

ggplotly(avp_scatter) %>%
  layout(autosize = T, margin = list(b = 50, r = 50, l = 50, t = 50)) %>%
  animation_opts(1000, transition = 0, redraw = FALSE)
```

@@

```{r, echo=F}
avp_scatter <- ggplot(sea_df, aes(x = actualRent, y = spt_Med, size = n1B, frame = listingQtr)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1) +
  scale_x_continuous(labels = scales::dollar) +
  scale_y_continuous(labels = scales::dollar) +
  xlab("Actual\n") +
  ylab("\nPredicted") +
  scale_size_area() +
  coord_equal() +
  theme_minimal()

ggplotly(avp_scatter) %>%
  layout(autosize = T, margin = list(b = 50, r = 50, l = 50, t = 50)) %>%
  animation_opts(1000, transition = 0, redraw = FALSE)
```
